Graph-based Neuron Agglomeration using 3D Skeletons

### 2017-11-06 papers/cvpr2018/2_method.tex

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to label segments from the segmentation and the edges between segments considered for merging.
Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
We locate merge candidates and produce corresponding edges based on these skeletons.
A CNN generates the edge weights by learning a merge function given two segments as input. 
A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm. (INSERT FIGURE HERE)

@@

We transform the extracted cubes for input into the neural network. 
The network takes three input channels for each voxel in the 3-D volume corresponding to the following mapping. 
Consider a pair of segments with labels $l_1$ and $l_2$ for every voxel $v$ in the region of interest. 
The first channel is $0.5$ if $v = l_1$ and $-0.5$ otherwise, the second channel is $0.5$ if $v = l_2$ and $-0.5$ otherwise, and the third channel is $0.5$ if $v = l_1$ or $v = l_2$ and $-0.5$ otherwise. 
Each 3-channel volume is subsequently downsampled into an array of size $(3, 22, 68, 68)$ using nearest-neighbor interpolation. 
Our neural network trains on these 4-D arrays to generate probabilities that $l_1$ and $l_2$ should merge.

>>>>

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
We locate merge candidates and produce corresponding edges based on these skeletons.
A CNN generates the edge weights by learning a merge function given two segments as input. 
A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm. (INSERT FIGURE HERE)

@@

The networks receives three input channels for every voxel in the region of interest around segments $l_1$ and $l_2$. 
The input to all of the channels is in the set $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.

### 2017-11-06 papers/cvpr2018/paper.tex

%%%%%%%%% TITLE
\title{Robust Agglomeration of Labeled Neurons using 3D Skeletonization}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
THE ABSTRACT
\end{abstract}

>>>>

%%%%%%%%% TITLE
\title{Graph-based Neuron Agglomeration using 3D Skeletons}

%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation not feasible. 
Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 
However, pixel-based segmentation results widely neglect global geometric properties.
We generate skeletons of membrane labels to approximate neural pathways in 3D. This allows us to efficiently apply graph-based optimization strategies and to train automatic classifiers for shape description against manually labeled ground truth. Our classifiers detect feasible and impossible neural pathways by looking at geometric properties alone, and are able to improve the segmentation labels accordingly. We demonstrate the performance of our classifiers on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. We discuss our findings and provide insights to learning shape features for neuron agglomeration.
\end{abstract}
